\documentclass[a4paper,12pt]{article} 
\setlength{\parindent}{0.0in}
\setlength{\parskip}{0.25in}

\usepackage{titlesec}
\titleformat{\subsection}[runin] {\normalfont\bfseries} {\thesubsection.}{.5em}{}[.---]
\titlespacing{\subsection} {\parindent}{1.5ex plus .1ex minus .2ex}{0pt}

\newcommand{\contractDay}{THEDAY }
\newcommand{\contractMonth}{THEMONTH }
\newcommand{\contractorName}{CONTRACTOR NAME }
\newcommand{\clientName}{CLIENT NAME }

\begin{document}
\part*{Production Agreement}

Parties

1.	\contractorName

2.	\clientName

\vspace{90 mm}


\newpage
Agreement dated the \contractDay day \contractMonth of 2010

Parties

\contractorName (``Contractor'') 

\clientName (``Client'')

\section*{Background}
The Client wishes to develop and produce [description of project or services] and the Contractor has the capacity and skills to provide the software and/or hardware development services necessary to carry out the project.

The parties, in consideration of the mutual covenants given, have agreed to enter into this Agreement to record the terms of the provision of those services.
\section*{Agreement}
\section{Definitions}
\textbf{Definitions:}  In this Agreement, unless a contrary intention appears, the definitions set out below shall apply:

\textbf{Agreement} Agreement means this agreement, any Statement of Work and all schedules and appendices attached to them.

\textbf{Business Day} means any day other than a Saturday, Sunday, or public holiday observed in London, England.

\textbf{Charges} means the amounts payable by the Client in respect of the Services, Hireage and Deliverables, as set out in a Statement of Work or as varied under this Agreement from time to time.

\textbf{Commencement Date} has the meaning set out in the Schedule 1.

\textbf{Confidential Information} means all information, know-how, ideas, concepts or business knowledge of a confidential nature relating to the business or systems of a party to this Agreement.

\textbf{Default Rate} means 5 per cent per annum above the Contractor’s cost of funds (expressed as an annual percentage rate) from whatever sources the Contractor may select, calculated on a daily basis.

\textbf{Deliverable} means, as the context requires, any service, item, software, documentation, or obligation that the Contractor agrees to deliver, develop, supply, modify, or perform under this Agreement in accordance with a Statement of Work.

\textbf{Delivery Date} means the dates set out in a Statement of Work, as modified by agreement in writing, by which a Service, Hardware or Deliverable shall be delivered to the Client.

\textbf{Designated Representative} means an authorised representative of a party, as specified in Schedule 1, and such replacement representative as may be notified by that party from time to time.

\textbf{Event} means the event as described in a Statement of Work.

\textbf{Event Date} means the dates set out in a Statement of Work, as modified by agreement in writing, for when an Event is scheduled to take place.

\textbf{Hardware} means any hardware as described in a Statement of Work.

\textbf{Hireage} means the hireage of any Hardware required as described in a Statement of Work.

\textbf{Intellectual Property} means all trade marks (including logos), domain names, copyright, patents, registered designs, circuit layouts, rights in computer software, databases and lists, rights in inventions, knowhow, and trade secrets, operating manuals, quality manuals and all other intellectual property, in each case whether registered or unregistered (including applications for the grant of any of the foregoing or right to apply for registration) and all rights or forms of protection having equivalent or similar effect to any of the foregoing which may subsist anywhere in the world, and all rights of action, powers and benefits of the same and Intellectual Property Rights shall have a corresponding meaning.

\textbf{Project} means the project as described in a Statement of Work.

\textbf{Requirements} means the agreed specifications for the Services, Hireage or Deliverables, that are set out in a Statement of Work or as may be agreed in writing by the parties from time to time.

\textbf{Service} means any service or obligation that the Contractor agrees to perform under this Agreement in accordance with a Statement of Work.

\textbf{Software} means any open source or proprietary code that forms part of the Deliverables.

\textbf{Statement of Work} means a statement of work agreed in writing between the parties, which identifies the Services, Hireage and Deliverables to be provided by the Contractor in respect of a Project or Event, in the form set out in Schedule 2.

\textbf{Term} means the period of this Agreement as set out in Schedule 1.

\textbf{VAT} means any value added tax payable in accordance with applicable statutory requirements.

\section{Term and exclusivity}
\subsection{Commencement and Term:} This Agreement shall commence on the Commencement Date and shall continue for the Term unless sooner terminated under clause 17.
\subsection{Non-exclusive:}  Except to the extent expressly set out in a Statement of Work, the Contractor is:
a non-exclusive supplier to the Client, and nothing in this Agreement shall prevent the Contractor from performing any services, supplying any deliverables or hiring any hardware to any other person; and
under no obligation to perform any services, to supply any deliverables or hire any hardware to the Client.
\section{Contractor’s Obligations}
\subsection{Prime contractor:}  In consideration of payment of the Charges, the Contractor shall, in accordance with, and pursuant to, the terms of this Agreement, supply the Services and Deliverables and hire the Hardware that meets the Requirements and in accordance with the Delivery Dates.  
\subsection{Subcontractors:}  The Contractor shall be responsible for Services, Deliverables and Hardware performed or supplied by its contractors or subcontractors.  
\subsection{Documentation:}  The Contractor shall supply all documentation (including source code and explanatory materials) relating to any Service, Deliverable or Hardware as specified in a Statement of Work.  
\section{Bleeding Edge Technology}
\subsection{Bleeding Edge:}  The use of the Software and Hardware to deliver the Services involves the creation of new technology known as “bleeding edge technology”.
\subsection{Risks:}  The Contractor shall carry out its obligations with care, skill and diligence, but the Client acknowledges and accepts that there are inherent performance and reliability risks associated with bleeding edge technology.  The Client further acknowledges that the venue and environment chosen or created for the Event will affect the performance of the Services.  
\subsection{Costs:}  The Contractor will use reasonable measures to mitigate the risks anticipated, but the Client acknowledges that some risks associated with bleeding edge technology are unavoidable or unforeseeable and that there are likely to be added costs or expenses associated with such technology.
\subsection{No warranties:}  In light of the unique nature of the Services and the Software, the Contractor gives no warranties whatsoever of any kind, express or implied, including but not limited to, the warranties of merchantability and fitness for a particular purpose.  


[Drafting note:  It is an option to delete clause 4.4 if client is not happy with such an explicit exclusion.  You then rely on the client’s acceptance that there are inherent performance and reliability risks (cl 4.2) to restrict your obligations if things go wrong.  Your position is not quite as strong, but you are still not in a position where you are giving guarantees of performance etc.] 

\section{Charges and Payment}
\subsection{Charges:} The Charges specified in a Statement of Work may be reviewed by the Contractor from time to time, and may be varied on 20 Business Days notice to the Client.
\subsection{Disbursements:} The Client shall be liable for the Contractor’s reasonable disbursements.
\subsection{Invoices:}  The Contractor shall invoice the Client for the Services, Deliverables and Hardware performed or supplied on a monthly basis during the Term.   

[Drafting note:  The SoW has been amended to allow for fixed price projects.  But this raises a couple of points.  Do we need to provide for change of scope provisions on fixed price projects to restrict your risk for ‘scope creep’ and allow you to renegotiate price?  Do we need delivery/acceptance provisions for fixed price payments?]

\subsection{Payment terms:}  All payments by the Client will be:
\begin{enumerate}
\item without any set-off, counterclaim or condition; and
\item without any deduction or withholding for any tax or any other reason, unless the Client is required to make a deduction or withholding by applicable law and the Client provides the original receipts (and any other relevant documentation) for the amount withheld or paid to the relevant taxation authority to the Contractor.
\end{enumerate}

\subsection{Bank Account:}  Unless otherwise agreed, all payments to be made to the Contractor will be made by deposit to a bank account nominated in writing by the Contractor by way of standing instruction to the Client.
\subsection{Due date:}  Each invoice shall be payable [within 10 Business Days of receipt] or [on the 20th day of the month following the date of the invoice].  If the due date for payment of an invoice is not a Business Day, the due date for payment will be the nearest preceding Business Day.
\subsection{Interest:}  Without prejudice to any other rights and remedies of the Contractor, interest calculated at the Default Rate will accrue on any moneys payable which are unpaid by the due date and will accrue from day to day on and from the date when the moneys were due for payment until, but not including, the date the payment is made. 
\subsection{Disputed Invoices:}   If the Client disputes any amount in any invoice, the Client shall notify the Contractor accordingly giving reasons for the dispute.  If the dispute cannot be resolved within 10 Business Days, the dispute will be resolved in accordance with clause 19.  The Client shall pay the undisputed portion of any disputed invoice in accordance with this clause 4.  The Contractor will continue to supply the Services, Deliverables and Hardware, notwithstanding any such dispute, provided that any disputed amount which is subsequently found to be payable will be paid no later than 10 Business Days after resolution of the dispute. 
\subsection{Taxes:}  All Charges are inclusive of all taxes, duties, fees and other charges but do not include VAT.  Unless expressly stated otherwise, all sums payable under this Agreement are stated exclusive of VAT, which shall be paid (if applicable) by the Client at the time of supply upon receipt of a valid VAT invoice. 

\section{Designated Representatives}
\subsection{Designated Representatives:}  Each party shall provide a Designated Representative (or an agreed substitute) as a primary point of contact for the duration of this Agreement.  The Designated Representatives shall have necessary authority on behalf of their respective parties to agree all matters between the parties in relation to this Agreement except as otherwise provided in this Agreement.  The Designated Representatives shall meet as agreed from time to time to further working relations under this Agreement and to discuss any issues that may have arisen.
\section{Intellectual Property}
\subsection{Pre-existing Intellectual Property:}  Except to the extent expressly set out in this Agreement, this Agreement does not transfer ownership of Intellectual Property Rights that may subsist in any items in existence prior to the date of this Agreement (“pre-existing Intellectual Property”).  

[Drafting note:  libraries, etc. that you create during the term of the project are not ‘pre-existing’.  This clause is aimed squarely at a piece of code or other IP that you have created and that you will use again as a starting point for a number projects.  But, as drafted, this agreement gives you full rights to IP you create during the term of the agreement as well.]

\subsection{Incorporation of proprietary materials:} If the Contractor incorporates into any Deliverable any pre-existing Intellectual Property or third party proprietary material, the Contractor shall grant, or procure the granting of, a non-exclusive licence for the Client to use the same for the Event.
\subsection{New Intellectual Property:}  Subject to clause 8, the rights, title and interests in Intellectual Property Rights that may subsist in any Deliverable or any other item (including information, computer programs, data, objects, source code, and documentation) that the Contractor creates at the Client’s request, or that come into existence through the performance of the Services, shall remain property of the Contractor.  

\section{Software}
\subsection{Code:}  The Software may contain both open source code and proprietary code.  The Contractor will inform the Client which type or types of code comprise the Software.
\subsection{Open Source:}  Open source code is available and licensed under terms set out by the owner of that code.  Each party shall ensure that it complies with the licence terms for any and all open source code, and shall indemnify the other party for any liability, costs or loss arising from that party’s breach of such licence terms.  The Contractor shall inform the Client of all open source code included in the Software.
\subsection{Proprietary Code:}  Proprietary code is written by the Contractor and, except as expressly set out in a Statement of Work, the Contractor retains all Intellectual Property Rights in all proprietary code written by the Contactor.  The Contractor grants the Client a non-exclusive, royalty-free, perpetual licence to use such Intellectual Property for the Event. 
\section{Hardware Hireage}
The Contractor agrees to hire to the Client the Hardware for the Hireage period to be used in conjunction with the Software.
The Contractor retains all rights, title and interests in the Hardware at all times, but the Hardware is at the Client’s risk and it is the Client’s responsibility to ensure that the Client looks after and insures (where necessary) the Hardware.
\section{Return of Hardware}
At the conclusion of the Hireage period, the Client will return the Hardware, and any other goods hired to the Client, to the Contractor.  The Client must ensure that the Contractor receives the Hardware, allowing fair wear and tear, in substantially the same condition as when the Client received the Hardware.
The Client is responsible for ensuring safe delivery of the Hardware to the Contractor.  The Contractor will assess the condition of the Hardware based on its condition when it receives the Hardware.
The Client is liable for any damage to the Hardware.  The Contractor will invoice the Client for any damage assessed.  The Client fully indemnifies and agrees to keep indemnified the Contractor for any cost, loss or damages incurred in respect of loss of, or damage to, the Hardware.

\section{Interface of Software and Hardware}
The Client acknowledges and accepts that:
\begin{enumerate}
\item the Hardware and Software need to be used in conjunction with each other in order for the Requirements to be met, and the Services to be performed, satisfactorily; and
\item the satisfactory delivery of the Services at an Event is wholly conditional upon the oversight of a person or persons with the requisite knowledge and skill as set out in the Statement of Work.  
\end{enumerate}
\section{Content}
\subsection{Warranty:}  The Client warrants that it has the right to use all Intellectual Property in the content that it provides to the Contractor and that forms any part of the Deliverables.
\subsection{Right to refuse:}  The Contractor may refuse any material that forms part of the Client’s content as part of the Deliverables for any reason, including material that is pornographic, is overtly violent, contains racially or religiously offensive material or that is objectionable in any way, at the sole discretion of the Contractor.
\subsection{Indemnity:}  The Client fully indemnifies and agrees to keep indemnified the Contractor for any loss, claim or proceeding brought as a result of the Client’s breach of, or use of material contemplated by, this clause 12.
\section{Confidential Information}
\subsection{Confidentiality:}  Each party will keep secret and confidential at all times all Confidential Information relating to the other party of which it, or its employees, contractors, or agents may become aware and will not communicate, cause to be communicated, copy, make available or re-supply any Confidential Information to any person other than those of its employees, contractors, or agents to whom disclosure is necessary for the purposes of this Agreement without the prior written consent of the other party.  Each party will use Confidential Information of the other party only for the purpose of completing its obligations under this Agreement.  Each party will take steps with its employees, contractors, and agents to ensure that none of them uses any Confidential Information in a manner not authorised by this Agreement or discloses the same to any person without the prior written consent of the other party.
\subsection{Exclusions:}  The obligations of each recipient party to whom Confidential Information is disclosed in clause 13.1 above shall not apply to any Confidential Information which is:
\begin{enumerate}
\item or at any time becomes, available to the public through no fault of that recipient party; or 
\item lawfully disclosed to such recipient party by third parties not under confidentiality obligations; or 
\item independently developed by the recipient party without the use of the other party’s Confidential Information; or
\item required to be disclosed by the recipient party by law.  
\end{enumerate}

\subsection{Security measures:}  Each party shall implement and maintain suitable procedures and security measures to ensure that all Confidential Information in that party’s possession or control is protected at all times from unauthorised disclosure, access, use, modification, damage or destruction by any person.
\subsection{Notification of breach of confidentiality:}  Each party shall promptly notify the other of the loss of any items containing Confidential Information and of any circumstances of which it becomes aware concerning any unauthorised possession, disclosure or use of any Confidential Information of the other party.
\section{Contractor’s Self Promotion}
\subsection{Licence to Self-Promote:}  The Client grants the Contractor a licence to use any part of the Deliverables, or any footage of the Event (footage only as mutually agreed by the parties) for the following purposes:
\begin{enumerate}
\item to enter any competitions or awards and for its use in any material published in connection with promoting those competitions or awards; and
\item to advertise or otherwise promote the Contractor’s work, including on the Contractor’s website. 
\end{enumerate}

\section{Liability}
\subsection{Exclusion:}  Subject to clause 12, neither party shall be liable for any loss of profits, or indirect, incidental or consequential loss or damage of any kind whatsoever arising under or in connection with this Agreement or any termination of this Agreement.  The Contractor excludes all liability relating to the Software, the Hardware, the Services and the Deliverables, including, but not limited to, any claim in contract, tort, product liability, statute or otherwise.  
\subsection{Limitation:}  The Contractor’s aggregate liability to the Client for all claims arising under or in connection with this Agreement or any Event shall not exceed the total Charges paid by the Client from time to time under this Agreement.  

\section{Force Majeure}
\subsection{Force majeure:}  Neither party shall be liable for any delay in meeting, or failure to meet, its obligations under this Agreement to the extent that such delay or failure is caused by any event outside its reasonable control (including, without limitation, any delay or failure caused by any act or omission of the other party).

\section{Termination}
\subsection{Termination for default:}  Either party may terminate this Agreement by notice in writing to the other if:
\begin{enumerate}
\item the other party has materially breached any of its obligations under this Agreement and fails to remedy the breach within 20 Business Days after written notice from the non-defaulting party specifying the breach and requiring it to be remedied; or
\item the other party becomes, or threatens to become, or is at substantial risk of becoming, subject to any form of insolvency administration including, without limitation, any resolution, procedure or proceedings relating to liquidation, inability to pay debts as they fall due, insolvency or appointment of a receiver, receiver and manager, liquidator, provisional liquidator, administrator statutory manager or similar officer, or if the other party makes an assignment for the benefit of its creditors.
\end{enumerate}

\subsection{Consequences of termination:}  If this Agreement is terminated or expires for any reason, then:
\begin{enumerate}
\item each party shall promptly return to the other party all documents, information and items of property belonging to the other party that are in that party’s possession or control; and
\item the Client shall pay the Contractor for Services, Hireage and Deliverables properly supplied by the Contractor down to the date of termination, but otherwise the parties shall be regarded as discharged from any further obligations under this Agreement and under a Statement of Work.  
\end{enumerate}
\subsection{Survival of clauses:}  The termination of this Agreement for any reason shall not affect the validity and enforceability of any rights of a party against the other party which have accrued up to and including the date of termination.
\section{Notices}
\subsection{Address for Notices:}  A notice, consent or approval to be given under this Agreement (a “Notice”) may by given by one party to the other party by personally serving it on that party, or by sending it by post to that party, or by submitting it by facsimile or email in accordance with the contact details set out in Schedule 1 (or such other contact details as the party to be notified may advise for the purpose from time to time).
\subsection{Deemed receipt:} Unless there is sufficient evidence to the contrary, any Notice will be deemed to be given:
\begin{enumerate}
\item if personally served, upon receipt by an officer or other duly authorised employee, agent or representative of the receiving party; 
\item if sent by post, two Business Days after it is posted;
\item if sent by facsimile, upon its receipt, as to which a confirmation slip or other confirmation of transmission shall be adequate proof of receipt; or
\item if sent by email, upon delivery of the email to the designated email server of the party receiving the Notice,
\end{enumerate}
provided that the Notice will be deemed to have been received on the next Business Day if the Notice is served, or sent by facsimile or email, on a day that is not a Business Day (or if that Notice is served or sent after 5:00pm on a Business Day).

\section{Dispute Resolution}
\subsection{General:}  The parties undertake to use all reasonable efforts in good faith to resolve any dispute which arises between them in connection with this Agreement.  A party will as soon as reasonably practicable give the other a notice of any such dispute.
\subsection{Internal dispute resolution:} Any dispute will be referred:
initially to the Designated Representatives of the parties, who will endeavour to resolve the dispute within five Business Days of the giving of the dispute being referred to them; and
if the Designated Representatives do not resolve the dispute within the time referred to in clause 19.2(a), to the representatives of the respective Chief Executives of the parties, who will endeavour to resolve the dispute, within a further five Business Days.
\subsection{Mediation:}  If, following the relevant internal dispute resolution procedure referred to in clause 19.2, the parties fail to resolve the dispute, then the parties will use best endeavours to settle their dispute by mediation before resorting to litigation.  Either party may initiate mediation in the United Kingdom by giving written notice to the other party.  The mediator should be agreed by the parties, but if the parties cannot agree on one within five Business Days after the mediation has been initiated, then the mediator shall be selected by the Chair for the time being of the Law Society of England and Wales (or his or her nominee) or its successor.
\subsection{Not arbitration:}  Clauses 19.2 and 19.3 provide for a form of alternative dispute resolution and are not references to arbitration.
\subsection{Continuing performance:} Pending the final settlement of any dispute, the parties shall continue to perform their respective obligations under this Agreement as far as possible as if no dispute had arisen.
\subsection{Judicial proceedings:}  No formal proceedings for the judicial resolution of any relevant dispute between the parties may be commenced until the dispute has gone through the relevant internal dispute resolution process under clause 19.2, and the mediation process under clause 19.3 has been completed.
\subsection{Venue:}  Any dispute resolution procedures shall be held in London, United Kingdom, unless otherwise agreed in writing.
Injunctive relief:  Notwithstanding anything in this clause 19, a party may commence court proceedings in relation to any dispute, controversy or claim arising under or in connection with this Agreement at any time where that party seeks urgent injunctive relief.

\section{Non- solicitation}
\subsection{Client Non-Solicitation:} The Client shall not for a period of 6 months from the expiry or termination of this Agreement solicit, engage or employ any of the Contractor’s employees, officers or contractors with whom the Client had contact or dealings. 

\section{General}
\subsection{Assignment and subcontracting:}  Except as expressly provided for in this Agreement neither party may assign its rights or obligations under this Agreement without the prior written consent of the other party, which shall not be unreasonably withheld.
\subsection{Independent contractors:}  The parties to this Agreement shall act as independent contractors in the performance of their obligations under this Agreement.  The relationship between the parties shall not be deemed to be an employment relationship, partnership, or joint venture, and neither party shall act as agent for, or be able to take any action to legally bind, the other party for any purpose whatsoever.
\subsection{No waiver:}  Failure or neglect by a party to enforce at any time any of the terms, conditions or provisions of this Agreement shall not be construed to be a waiver of that party’s rights, or to in any way affect the validity of the whole or any part of this Agreement, or to otherwise prejudice that party’s rights to take subsequent action.  Any waiver by a party in respect of any right provided for in this Agreement shall not be construed to be a waiver of any further or future right arising under this Agreement.
\subsection{Amendment:}  No provision of this Agreement shall be changed, waived or modified, nor shall this Agreement be discharged in whole or in part except by an agreement in writing signed by the parties.
\subsection{No intention to confer benefits on other people:}  Nothing in this Agreement is intended to confer any benefit on anyone other than the parties.
\subsection{Severability: } If any provision of this Agreement is held invalid, unenforceable or illegal for any reason, that provision shall be deemed deleted and the remainder of this Agreement shall remain in full force and effect to the maximum possible extent.
\subsection{Governing law: }  This Agreement shall be governed by English law and the courts of England shall have nonexclusive jurisdiction to hear and determine all issues which may arise under or in relation to this Agreement.  The parties submit to the jurisdiction of the English courts and agree that the English courts are a convenient forum in which to resolve any dispute arising under or in relation to this Agreement. 
\subsection{Counterparts:}  This Agreement may be executed in two or more counterparts each of which will be deemed an original, but all of which together will constitute one and the same instrument.  A party may enter into this Agreement by signing any counterpart.
\subsection{Entire agreement:}  This Agreement constitutes the entire agreement between the parties and supersedes all prior communications, representations, agreements or understandings, either verbal or written, between the parties with respect to the subject matter of this Agreement.
\section{Interpretation}
\subsection{Scope of Agreement:}  This Agreement comprises these terms and conditions, including all schedules and appendices attached to them.  In the event of any conflict of meaning or ambiguity, the documents that comprise this Agreement shall have the descending order of precedence set out below:
\begin{enumerate}
\item any variation to a Statement of Work agreed in writing between the parties after the date of that Statement of Work;
a Statement of Work;
\item any variation to this Agreement agreed in writing between the parties after the date of this Agreement;
\item the terms of this Agreement;
\item the schedules.
\end{enumerate}
\subsection{Interpretation:}  For the purposes of interpretation and construction of this Agreement:
\begin{enumerate}
\item words importing the singular or plural number include the plural and singular number respectively;
\item references to clauses, sections and Schedules are references to clauses, sections and Schedules in or to this Agreement unless expressly stated otherwise;
\item headings are inserted for the sake of convenience of reference only and do not affect the interpretation of this Agreement;
\item references to the parties include (insofar as is consistent with this Agreement) their respective personnel, agents, contractors, and their respective successors in title and permitted assigns;
\item references to persons shall be deemed to include references to individuals, companies, corporations and any other association or organisations whether or not having separate legal personality; and
\item references to “include”, “includes”, and “including” must be read as if they are followed by the phrase “without limitation” regardless of whether or not they are in fact followed by that phrase.
\end{enumerate}


\textbf{In Witness} of which this agreement has been signed.\newline
\newline
\begin{tabular}{lll}
\textbf{Signed} for and on behalf of & ) & \\
\textbf{\clientName} & ) & ...................................................... \\
by & ) & \\
\end{tabular}

Witnessed by:\newline
\newline
\begin{tabular}{lll}
...................................................... & (signature and name) & \\
...................................................... & (occupation) & \\
...................................................... & (address) & \\
\end{tabular}

\begin{tabular}{lll}
\textbf{Signed by}	& ) & \\
\textbf{\contractorName}	& ) & ...................................................... \\
by a director	& ) & \\
& ) & \\
\end{tabular}

\newpage
\part*{Schedule 1}
\begin{Large}
Contract Details
\end{Large}

\begin{tabular}{ll}
Detail&\\
Value&\\
Commencement Date&[                 ] 2010\\
Term	&[     ]\\
Contact Details&\textbf{\clientName}\\
&Phone :	\\
&Fax : 	\\
&Email:	\\
\\
&\textbf{\contractorName}\\
&Phone :	\\
&Fax : 	\\
&Email:	\\
\\
Designated Representatives&\textbf{\clientName}\\
&..........................\\
&..........................\\
\\
&mailmo\textbf{\contractorName}\\
&..........................\\
&..........................\\
\end{tabular}

\newpage
\part*{Schedule 2}
\begin{Large}
Statement of Work
\end{Large}

Project:

Event and Event Dates:

Deliverables and Services: 

Charges:
The agreed Charges (on a time and materials basis) for the Services and Deliverables:
Contractor	Hourly rate (plus VAT if any)
	
	

Deliverable	Fixed Cost (plus VAT if any)
	
	

Hardware Hireage and Hire Period:
Hardware	Hire Period	Charges (plus VAT if any)
		

Delivery Dates:
Deliverable	Delivery Date	Comment
		

Personnel and other requirements:



Software Ownership Clauses:
1.	The Contractor retains all ownership rights in any new Proprietary Code and the Client is granted a non-revocable, non-exclusive and royalty-free licence to use any Proprietary Code in any way as the Client so wishes.
or
2.	The Client is granted all ownership rights in any new Proprietary Code and the Contractor is granted a non-revocable, non-exclusive and royalty-free licence to use any Proprietary Code in any way as the Contractor so wishes.
or
3.	The Client and the Contractor are each granted full ownership rights and privileges in any new Proprietary Code and each may use or exploit any Proprietary Code in any way as they wish without reference to the other.
[Drafting note: these clauses have been drafted widely:  “all Proprietry Code”.  You can also list specific bits to which these clauses apply] 

\end{document}